\Title

### 2021-05-12 latex/paper/main.tex
First edit of the simulation and experiment sections

The results of Theorem \ref{thm:acrobot-energy-stabilization} lead naturally to
the idea of energy regulation: one could employ a supervisor which switches
between injection and dissipation constraints to stabilize a desired energy
level \(\bar{E}\).
For instance, the supervisor could inject energy when \(E(q_u,p_u) < \bar{E}\) 
and dissipate energy when \(E(q_u,p_u) > \bar{E}\), with some hysteresis to
avoid infinite switching.

%/========== Experiments ==========/%
\section{Simulation Results}\label{sec:simulations}
In Section \ref{sec:experiments} we will test our VNHC on the physical acrobot
built by Xingbo Wang \cite{xingbo_thesis}.

Note that this acrobt does not correspond to the simple acrobot in Figure
\ref{fig:simple-acrobot-model}, but rather to the more general acrobot model in
Figure \ref{fig:acrobot-model}.
If we define 
\begin{align*}
    m_{11}(q) := &m_a l_u^2 + 2m_al_ul_{c_a}\cos(q_a) + m_al_{c_a}^2 +
    m_ul_{c_u}^2 \\
                 &+ J_u + J_a
                 , \\
    m_{12}(q) := &m_al_{c_a}^2 + m_al_ul_{c_a}\cos(q_a) + J_a
    , \\
    m_{22}(q) := &m_al_{c_a}^2 + J_a,
\end{align*}
then the inertia matrix and potential for the physical acrobot are
\begin{align*}
    M(q) &= \begin{bmatrix}
        m_{11}(q) & m_{12}(q) \\
        m_{12}(q) & m_{22}(q)
    \end{bmatrix}
    , \\
    V(q) &= g\big(m_al_{c_a}(1-c_{ua})
    + (m_al_u + m_ul_{c_u})(1-c_u)\big).
\end{align*}

@@

Evaluating the true mechanical energy of this acrobot at the VNHC
\(q_a = 0\) yields the energy of the nominal pendulum,
\[
    E(q_u,p_u) \approx 396.5501 p_u^2 + 0.5997(1 - \cos(q_u))
    .
\]

We will simulate our VNHC using the parameters of
this physical robot, which can be found in Table \ref{tab:acrobot-parameters}.
If our VNHC injects energy into this acrobot, then we can infer that
VNHCs are robust to model mismatch.

@@

According to Theorem \ref{thm:acrobot-energy-stabilization}, the control
parameter \(I\) must be small if one wants the VNHC to inject energy.
While we could make \(I\) arbitrarily small in simulations, we will eventually
implement this VNHC on a physical system where \(I\) must be large enough to
overcome friction in leg motor.
Setting \(\bar{q}_a = 1\), we experimentally determined that \(I = 10\) is a
viable control value for energy injection.

We simulated the acrobot with initial condition 
\((q_u,p_u) = \left(\pi/32,0 \right)\) for \(30\) seconds and plotted the
resulting orbit in Figure \ref{fig:acrobot-in-orbit}.

@@

To verify numerically that the acrobot would consistently achieve rotations, we
ran a Monte-Carlo simulation \cite{montecarlo} where we initialized the acrobot
randomly inside the sublevel set
\[
    \left\{(q_u,p_u) \in \SxR \mid
    E(q_u,p_u) \leq E\left(\frac{\pi}{32},0\right)\right\}
    ,
\] 
and measured how long it took to begin rotating.
The results in Figure \ref{fig:acrobot-mc} show that
the acrobot always rotated within 20--40 seconds.

\begin{figure}[]
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_mc.png}
    \caption{Monte Carlo simulation results.}
    \label{fig:acrobot-mc}
\end{figure}

@@

According to Theorem \ref{thm:acrobot-energy-stabilization}, a negative value
of \(I\) will dissipate energy from the acrobot.
To test this, we initialized our acrobot with a rotation at the phase
\((q_u,p_u) = (0,0.18)\),  set \(I = -10\), and simulated the constrained
dynamics for \(30\) seconds.
The resulting orbit is plotted in Figure \ref{fig:acrobot-diss-orbit}. 
As expected, the acrobot slows down over time.
We again highlight the locations where the orbit crossed the set \(E_\pi\) in
black, with the final crossing in red. 
After this crossing, the acrobot ceased rotating and its oscillations decayed to
zero.

@@

Once can use a simple supervisor to stabilize oscillations by appropriately
toggling between injection and dissipation VNHCs.
Specifically, one chooses a desired oscillation angle 
\(q_\text{des} \in \, ]0,\pi[\) and, to avoid infinite switching, a
hysteresis value \(\delta \in [0,1]\) 
Each time the orbit crosses the \(q_u\)-axis (i.e. \(p_u = 0\)) or 
when \(|q_u| = \pi\), the supervisor changes which VNHC is enforced as follows:
\begin{itemize}
    \item If \(|q_u| < (1-\delta)q_\text{des}\), enable the injection VNHC.
    \item If \(|q_u| > (1+\delta)q_\text{des}\), enable the dissipation VNHC.
    \item If \((1-\delta)q_\text{des} \leq |q_u| \leq (1+\delta)q_\text{des}\),
        keep the leg extended at \(q_a = 0\). This can be done continously since
        \(q_a = 0\) when \(p_u = 0\).
\end{itemize}

Figure \ref{fig:acrobot-osc-reg} shows the supervisor stabilizing an
oscillation with body angle \(q_\text{des} = \pi/2\) and a 
\(5\%\) hysteresis, meaning \(\delta = 0.05\).
The supervisor reevaluated its choice of VNHC at each black star;  
the red circle corresponds to the part of the orbit where the supervisor kept
the leg extended, because the oscillation was within tolerance of
\(q_\text{des}\).

In Figure \ref{fig:acrobot-osc-reg-in} the acrobot was initialized at 
\((q_u,p_u) = (\pi/32,0)\); here the supervisor injected energy for most of the
orbit.
In Figure \ref{fig:acrobot-osc-reg-diss} the acrobot was initialized at the rotation
\((q_u,p_u) = (0,0.19)\); here the supervisor dissipated energy. 
In both cases, the supervisor stabilized the desired oscillation .

@@

\subsection{Rotation Regulation}
Along with stabilizing oscillations, one can use a supervisor to stabilize
rotations.
In this case, one chooses a desired rotation rate \(p_\text{des} > 0\) and a
hystersis value \(\delta \in [0,1]\).
Each time the orbit crosses the \(p_u\)-axis (i.e. when \(q_u = 0\)), the
supervisor changes which VNHC is enforced as follows:
\begin{itemize}
    \item If \(|p_u| < (1-\delta)p_\text{des}\), enable the injection VNHC.
    \item If \(|p_u| > (1+\delta)p_\text{des}\), enable the dissipation VNHC.
    \item If \((1-\delta)p_\text{des} \leq |p_u| \leq (1+\delta)p_\text{des}\),
        extend the leg fully by setting \(q_a = 0\).
        For these simulations, we assume this can be done instantaneously.
\end{itemize}

Rotation regulation is demonstrated in Figure \ref{fig:acrobot-rot-reg}, where
the supervisor stabilizes \(p_\text{des} = 0.19\) with a \(2\%\) hysteresis 
\(\delta = 0.02\).
The supervisor changed its choice of VNHC at each black star until it finally extended
the leg (shown in red).

In Figure \ref{fig:acrobot-rot-reg-in} the acrobot was initialized at the
oscillation \((q_u,p_u) = (\pi/2,0)\); here the supervisor injected energy until
the orbit hit the \(p_u\)-axis near \(p_\text{des}\).
In Figure \ref{fig:acrobot-rot-reg-diss} the acrobot was initialized at the
faster rotation \((q_u,p_u) = (0, 0.23)\); the supervisor dissipated energy.
In both cases, the desired rotation was stabilized correctly.

@@

@@

\subsection{Hardware Description}
In this section we will demonstrate that our VNHC is robust to friction, sensor
noise, and other real-world considerations by testing it on the physical
acrobot built by Xingbo Wang \cite{xingbo_thesis} 
(Figure \ref{fig:xingbo-acrobot}.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{xingbo_acrobot.jpg}
    \caption{The acrobot built by Wang \cite{xingbo_thesis}.}
    \label{fig:xingbo-acrobot}
\end{figure}

This acrobot is comprised of two 3D-printed links: a torso and a leg.
The torso link houses an Arduino Nano microcontroller unit (MCU) which controls
a Dynamixel RX24F servo motor between the torso and the leg.
The MCU and the motor are powered by a 12V battery held in a compartment
in the leg.

@@

VNHC implementation requires full knowledge of the acrobot's phase. 
The rotary encoder directly measures \(q_u\), and the Dynamixel servo
motor provides measurements of \(q_a\).
However, there are no sensors measuring the velocity \(\dot{q}\), which means we cannot
directly evaluate \(p_u\) and \(p_a\).
To resolve this issue, the MCU estimates \(\dot{q}\) using sequential measurements of \(q\)
and a washout filter.
We then compute \(p = M(q)\dot{q}\) for use in the VNHC controller.

@@

The system was given the name SUGAR: Simple Underactuated Gymnastics and
Acrobatics Robot.
Its dynamic parameters are outlined in Table \ref{tab:acrobot-parameters}.

@@

In Section \ref{sec:simulations} we showed that VNHCs can be used for energy
injection, dissipation, and regulation. 
We will now demonstrate that VNHC-based giant motion is robust to external
disturbances by implementing our VNHC on the SUGAR system.
We performed the following tests.

\begin{enumerate}
    \item \textbf{Baseline Test:} 
    we initialized the acrobot at 
    \((q_u,p_u) \approx \left(\pi/8,0\right)\). 
    The resulting orbit in Figure \ref{fig:acrobot-unperturbed-orbit} shows
    the acrobot clearly gaining energy over time.
    Its motion looks similar to that of the energy injection simulation (Figure
    \ref{fig:acrobot-in-orbit}), though the acrobot appears to stop gaining
    energy once it reaches a rotation with energy \(E(0,0.195)\).

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_unperturbed_orbit.png}
    \caption{The physical acrobot's orbit during the baseline energy injection test.}
    \label{fig:acrobot-unperturbed-orbit}
\end{figure}

\item \textbf{Stop Test:}
    we initialized the acrobot at 
    \((q_u,p_u) \approx \left(\pi,0\right)\), let it run for 15
    seconds, then stopped it at the bottom of its arc.
    The resulting orbit is shown in Figure \ref{fig:acrobot-stopped-orbit}.
    The blue rotation curve corresponds to the orbit before the disturbance,
    while the red spiral confirms that the acrobot begins oscillating after it
    is stopped.  
    Despite the disturbance, it gains energy and eventually starts rotating
    again.

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_stopped_orbit.png}
    \caption{The physical acrobot's orbit before (blue) and after (red) stopping.}
    \label{fig:acrobot-stopped-orbit}
\end{figure}

\item \textbf{Push Test:}
    to see how the acrobot responds when pushed, we allowed
    the acrobot to rotate undisturbed for 15 seconds and then pushed it in its
    direction of motion.
    The orbit in Figure \ref{fig:acrobot-fpush-orbit} shows that the acrobot,
    when pushed, rotates with energy \(E(0,-0.22)\), but then slows down until
    it reaches a rotation with energy \(E(0,-0.195)\).
    We repeated this test by pushing the acrobot against its direction of motion.
    The orbit in Figure \ref{fig:acrobot-rpush-orbit} demonstrates that the acrobot
    readily changes direction, and quickly achieves its maximum speed
    with energy \(E(0,0.195)\).
\end{enumerate}

In simulation, the acrobot was able to gain energy even when initialized
with energy \(E(q_u,p_u) > E(0,0.195)\). 
The baseline and push tests suggest that our VNHC injects energy into the SUGAR
system only on \(\mathcal{O}_2(0.195)\).
This difference between simulation and implementation is likely due to
friction.

\begin{figure}
    \centering
    \begin{subfigure}[ht]{0.49\linewidth}
        \includegraphics[width=\linewidth]{acrobot_fpush_orbit.png}
        \caption{The forwards push test.}
        \label{fig:acrobot-fpush-orbit}
    \end{subfigure}
    \begin{subfigure}[ht]{0.49\linewidth}
        \includegraphics[width=\linewidth]{acrobot_rpush_orbit.png}
        \caption{The reverse push test.}
        \label{fig:acrobot-rpush-orbit}
    \end{subfigure}
    \caption{The acrobot orbit before (blue) and after (red) pushing.}
\end{figure}

We had hoped to show experimental results for dissipation and
oscillation/rotation regulation, but unfortunately our Dynamixel RX24F servo
motor broke before we could perform these experiments.
These motors are no longer in production at the time of writing, so the SUGAR
system has been retired for the time being.

\subsection{Summary of Results} 
We performed three tests on the SUGAR system: a baseline energy injection test,
a stop test, and a push test.
These experiments demonstrate that VNHC-based energy injection is robust to
significant model mismatch, friction, sensor noise, discretized control
implementation, rate-limited measurement and control signals, and dramatic
external disturbances.

>>>>

One can use the results of Theorem \ref{thm:acrobot-energy-stabilization} 
for energy regulation.
For example, one might employ a supervisor which switches
between injection and dissipation VNHCs to stabilize a desired energy
level \(E_\text{des}\), with some hysteresis to avoid infinite switching.
We will explore this idea in Section \ref{sec:simulations}.

%/========== Experiments ==========/%
\section{Simulation Results}\label{sec:simulations}
In Section \ref{sec:experiments} we will test our VNHC on the physical acrobot
built by Xingbo Wang \cite{xingbo_thesis}.
This physical acrobot cannot be modelled by the simplified setup in Figure
\ref{fig:simple-acrobot-model}, because the torso and leg links have 
distributed mass. 
We must therefore use the more general acrobot model in Figure
\ref{fig:acrobot-model} to represent this system.
If we define 
\begin{align*}
    m_{11}(q) := &m_a l_u^2 + 2m_al_ul_{c_a}\cos(q_a) + m_al_{c_a}^2 +
    m_ul_{c_u}^2 \\
                 &+ J_u + J_a
                 , \\
    m_{12}(q) := &m_al_{c_a}^2 + m_al_ul_{c_a}\cos(q_a) + J_a
    , \\
    m_{22}(q) := &m_al_{c_a}^2 + J_a,
\end{align*}
where \(J_u\) and \(J_a\) are the moments of inertia of the torso and leg links
respectively, then the inertia matrix becomes
\begin{equation*}
    M(q) = \begin{bmatrix}
        m_{11}(q) & m_{12}(q) \\
        m_{12}(q) & m_{22}(q)
    \end{bmatrix}
    ,
\end{equation*}
and the potential function is
\begin{equation*}
    V(q) = g\big(m_al_{c_a}(1-c_{ua})
    + (m_al_u + m_ul_{c_u})(1-c_u)\big)
    .
\end{equation*}

@@

The dynamic parameters of Wang's acrobot can be found in Table
\ref{tab:acrobot-parameters}.
Evaluating the mechanical energy of an acrobot with these parameters
at the VNHC \(q_a = 0\) yields the mechanical energy of the nominal pendulum,
\[
    E(q_u,p_u) \approx 396.5501 p_u^2 + 0.5997(1 - \cos(q_u))
    .
\]

We will now simulate the effects of constraining Wang's acrobot with
~\eqref{eqn:acrobot-constraint}, thereby demonstrating that VNHCs are robust to
model mismatch.
According to Theorem \ref{thm:acrobot-energy-stabilization}, the control
parameter \(I\) must be ``small" for our VNHC to inject (or dissipate) energy
into the simplified acrobot. 
Unfortunately, the Theorem does not specify how small \(|I|\) must be;
while we could make it arbitrarily small in simulations, we will eventually
implement this VNHC on a physical testbed where \(|I|\) must be large enough to
overcome friction in the leg motor.

Setting \(\bar{q}_a = 1\), we experimentally determined that \(|I| = 10\) is a
viable control parameter, so this is the value we will use for all simulations
and experiments.
In other words, our injection VNHC is ~\eqref{eqn:acrobot-constraint} with 
\(I = 10\) while our dissipation VNHC is ~\eqref{eqn:acrobot-constraint} with 
\(I = -10\).

@@

We simulated the acrobot constrained by our injection VNHC
with initial condition \((q_u,p_u) = \left(\pi/32,0 \right)\) for \(30\)
seconds, and plotted the resulting orbit in Figure \ref{fig:acrobot-in-orbit}.

@@

To verify numerically that the acrobot would consistently achieve rotations, we
ran a Monte-Carlo \cite{montecarlo} simulation where we initialized the acrobot
randomly inside the sublevel set
\[
    \left\{(q_u,p_u) \in \SxR \mid
    E(q_u,p_u) \leq E\left(\frac{\pi}{32},0\right)\right\}
    ,
\] 
and measured how long it took to begin rotating.
The results in Figure \ref{fig:acrobot-mc} show that
the acrobot always rotated within 20--40 seconds.

\begin{figure}[]
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_mc.png}
    \caption{Monte Carlo simulation for energy injection.}
    \label{fig:acrobot-mc}
\end{figure}

@@

We initialized our acrobot with a rotation at \((q_u,p_u) = (0,0.18)\) and
simulated the constrained dynamics (under the dissipation VNHC) for \(30\)
seconds.
The resulting orbit is plotted in Figure \ref{fig:acrobot-diss-orbit}. 
As expected, the acrobot slows down over time.
We highlight the locations where the orbit crossed the set \(E_\pi\) by
black stars, with the final crossing in red.
After this crossing, the acrobot ceased rotating and its oscillations decayed to
zero.

@@

Once can use a supervisor to stabilize oscillations by appropriately
toggling between injection and dissipation VNHCs.
Specifically, one chooses a desired oscillation angle 
\(q_\text{des} \in \, ]0,\pi[\) and, to avoid infinite switching, a
hysteresis value \(\delta \in [0,1]\).
Each time the orbit crosses the \(q_u\)-axis (i.e. when \(p_u = 0\)) or 
when \(|q_u| = \pi\), the supervisor does the following: 
\begin{itemize}
    \item If \(|q_u| < (1-\delta)q_\text{des}\), enable the injection VNHC.
    \item If \(|q_u| > (1+\delta)q_\text{des}\), enable the dissipation VNHC.
    \item If \((1-\delta)q_\text{des} \leq |q_u| \leq (1+\delta)q_\text{des}\),
        keep the leg extended at \(q_a = 0\). This can be done continously since
        \(q_a = 0\) when \(p_u = 0\).
\end{itemize}

Figure \ref{fig:acrobot-osc-reg} shows the supervisor stabilizing an
oscillation with body angle \(q_\text{des} = \pi/2\) and a 
\(5\%\) hysteresis, meaning \(\delta = 0.05\).
The supervisor reevaluated its choice of VNHC at each black star;  
the red contour corresponds to the part of the orbit where the supervisor kept
the leg extended, because the oscillation was within tolerance of
\(q_\text{des}\).
The solid black line is the desired oscillation, and the dashed black
lines show the hysteresis around that orbit.

In Figure \ref{fig:acrobot-osc-reg-in} the acrobot was initialized at 
\((q_u,p_u) = (\pi/32,0)\); here the supervisor injected energy for most of the
orbit.
In Figure \ref{fig:acrobot-osc-reg-diss} the acrobot was initialized at the rotation
\((q_u,p_u) = (0,0.19)\); here the supervisor dissipated energy. 
In both cases, the supervisor stabilized the desired oscillation.

@@

\subsection{Rotation Regulation}
One can also use a supervisor to stabilize rotations.
In this case, one chooses a desired rotation rate \(p_\text{des} > 0\) and a
hysteresis value \(\delta \in [0,1]\).
Each time the orbit crosses the \(p_u\)-axis (i.e. when \(q_u = 0\)), the
supervisor changes which VNHC is enforced as follows:
\begin{itemize}
    \item If \(|p_u| < (1-\delta)p_\text{des}\), enable the injection VNHC.
    \item If \(|p_u| > (1+\delta)p_\text{des}\), enable the dissipation VNHC.
    \item If \((1-\delta)p_\text{des} \leq |p_u| \leq (1+\delta)p_\text{des}\),
        extend the leg fully by setting \(q_a = 0\).
        For these simulations, we assume this can be done instantaneously.
\end{itemize}

Rotation regulation is demonstrated in Figure \ref{fig:acrobot-rot-reg}, where
the supervisor stabilizes \(p_\text{des} = 0.19\) with a \(2\%\) hysteresis 
\(\delta = 0.02\).
The supervisor changed its choice of VNHC at each black star until it was within
range of \(p_\text{des}\), at which point it extended the leg (shown in red).

In Figure \ref{fig:acrobot-rot-reg-in} the acrobot was initialized at 
\((q_u,p_u) = (\pi/2,0)\); here the supervisor injected energy until
the orbit hit the \(p_u\)-axis near \(p_\text{des}\).
In Figure \ref{fig:acrobot-rot-reg-diss} the acrobot was initialized at the
faster rotation \((q_u,p_u) = (0, 0.23)\); the supervisor dissipated energy.
In both cases, the desired rotation was stabilized correctly.

@@

Note the difference in shape between the blue rotations of the dissipation VNHC
and the red rotation of the nominal pendulum: the red one slows down much more
near \(|q_u| = \pi\).
This difference arises because of the size of \(I\):
if \(|I|\) were smaller, the blue rotations would be more similar in shape to the
red one because the constrained dynamics for the dissipation VNHC would be
well approximated by the nominal pendulum.

@@

\subsection{Hardware Description}
In this section we will demonstrate that our VNHC is robust to friction, sensor
noise, and other real-world considerations by testing it on the physical
acrobot built by Xingbo Wang \cite{xingbo_thesis} 
(Figure \ref{fig:xingbo-acrobot}).
This platform was given the name SUGAR, which stands for
Simple Underactuated Gymnastics and Acrobatics Robot.
Its dynamic parameters are outlined in Table \ref{tab:acrobot-parameters}.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{xingbo_acrobot.jpg}
    \caption{SUGAR is the physical acrobot built by Wang \cite{xingbo_thesis}.}
    \label{fig:xingbo-acrobot}
\end{figure}

SUGAR is comprised of two 3D-printed links: a torso and a leg.
The torso link houses an Arduino Nano microcontroller unit (MCU) which controls
a Dynamixel RX24F servo motor between the torso and the leg.
The MCU and the motor are powered by a 12V battery held in a compartment
in the leg.

@@

The rotary encoder directly measures \(q_u\), and the Dynamixel servo
motor provides measurements of \(q_a\).
However, there are no sensors measuring the velocity \(\dot{q}\), which means we cannot
directly evaluate \(p_u\) and \(p_a\).
To resolve this issue, the MCU estimates \(\dot{q}\) using sequential measurements of \(q\)
and a washout filter.
We then compute \(p = M(q)\dot{q}\) for use in the VNHC controller.

@@

@@

We performed the following tests on SUGAR.

\begin{enumerate}
    \item \textbf{Baseline Test:} 
    we initialized the acrobot at 
    \((q_u,p_u) \approx \left(\pi/8,0\right)\). 
    The resulting orbit in Figure \ref{fig:acrobot-unperturbed-orbit} shows
    that SUGAR clearly gaining energy over time.
    Its motion looks similar to that of the energy injection simulation (Figure
    \ref{fig:acrobot-in-orbit}), though its energy gain ceases once it reaches a
    rotation with energy \(E(0,0.195)\).

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_unperturbed_orbit.png}
    \caption{SUGAR's orbit during the baseline energy injection test.}
    \label{fig:acrobot-unperturbed-orbit}
\end{figure}

\item \textbf{Stop Test:}
    we initialized SUGAR at 
    \((q_u,p_u) \approx \left(\pi,0\right)\), let it run for 15
    seconds, then stopped it at the bottom of its arc.
    The resulting orbit is shown in Figure \ref{fig:acrobot-stopped-orbit}.
    The blue rotation curve corresponds to the orbit before the disturbance,
    while the red spiral confirms that the acrobot begins oscillating after it
    is stopped.  
    Despite the disturbance, it gains energy and eventually starts rotating
    again.

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_stopped_orbit.png}
    \caption{SUGAR's orbit before (blue) and after (red) stopping.}
    \label{fig:acrobot-stopped-orbit}
\end{figure}

\item \textbf{Push Test:}
    to see how SUGAR responds when pushed, we allowed
    it to rotate undisturbed for 15 seconds and then pushed it in its
    direction of motion.
    The orbit in Figure \ref{fig:acrobot-fpush-orbit} shows that the acrobot,
    when pushed, rotates with energy \(E(0,-0.22)\), but then slows down until
    it reaches a rotation with energy \(E(0,-0.195)\).
    We repeated this test by pushing SUGAR against its direction of motion.
    The orbit in Figure \ref{fig:acrobot-rpush-orbit} demonstrates that the acrobot
    readily changes direction, and quickly achieves its maximum speed
    with energy \(E(0,0.195)\).
\end{enumerate}

In simulation, the acrobot was able to gain energy even when initialized
with energy \(E(q_u,p_u) > E(0,0.195)\). 
The baseline and push tests suggest that our VNHC injects energy into SUGAR
only on \(\mathcal{O}_2(0.195)\).
This difference between simulation and implementation is likely due to
friction.

\begin{figure}
    \centering
    \begin{subfigure}[ht]{0.49\linewidth}
        \includegraphics[width=\linewidth]{acrobot_fpush_orbit.png}
        \caption{The forwards push test.}
        \label{fig:acrobot-fpush-orbit}
    \end{subfigure}
    \begin{subfigure}[ht]{0.49\linewidth}
        \includegraphics[width=\linewidth]{acrobot_rpush_orbit.png}
        \caption{The reverse push test.}
        \label{fig:acrobot-rpush-orbit}
    \end{subfigure}
    \caption{SUGAR's orbit before (blue) and after (red) pushing.}
\end{figure}

We had hoped to show more experimental results for dissipation and
oscillation/rotation regulation, but unfortunately the Dynamixel RX24F servo
motor broke before we could perform these experiments.
These motors are no longer in production at the time of writing this article, so
SUGAR met an untimely end to its career.

\subsection{Summary of Results} 
We performed three tests on SUGAR: a baseline energy injection test,
a stop test, and a push test.
These experiments demonstrate that VNHC-based energy injection is robust to
significant model mismatch, friction, sensor noise, discretized control
implementation, rate-limited measurement and control signals, and dramatic
external disturbances.
